Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-19 Answers_for_reviewers.tex

\documentclass[a4paper,french,english,10pt]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
%\usepackage{geometry}
%\geometry{verbose,a4paper,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm,headheight=3cm,headsep=3cm}
\usepackage{babel}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epsfig}
%\usepackage{esint}
\usepackage{color}
\usepackage{amsfonts}
\usepackage{amssymb,latexsym}
\usepackage{amscd}
\usepackage{multirow}
\usepackage{amsthm}
\usepackage[pdftex,bookmarks=true,bookmarksopen=true,colorlinks=true,linkbordercolor=white, citecolor=blue, linkcolor=red]{hyperref}

\usepackage{comment}

\newcommand{\dr}{\partial_R}
\newcommand{\ds}{\displaystyle}
\newcommand{\dz}{\partial_Z}
\newcommand{\dphi}{\partial_{\phi}}
\newcommand{\ephi}{\mathbf{e}_{\phi}}
\newcommand{\dt}{\partial_t}
\newcommand{\lp}{\triangle_{pol}}
\newcommand{\lpp}{\triangle_{pol}^2}
\newcommand{\gradp}{\nabla_{pol}}
\newcommand{\lpm}{\triangle_{pol}^{-1}}
\newcommand{\gs}{\triangle^{*}}
\newcommand{\U}{\mathbf{U}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\vB}{\mathbf{B}}
\newcommand{\vJ}{\mathbf{J}}
\newcommand{\vE}{\mathbf{E}}
\newcommand{\rot}{\nabla \times}
\newcommand{\er}{\mathbf{e}_R}
\newcommand{\ez}{\mathbf{e}_Z}
\newcommand{\eps}{\varepsilon}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\begin{document}

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est & IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-03-19 Corrected_version.tex
first corrections

We address the convergence analysis  on unstructured meshes
of diffusion
asymptotic preserving schemes for the discretization
of a problem with a stiff parameter denoted as $\eps\leq 1$.
The model problem considered in this work
is  the hyperbolic heat equation in the domain 
$t\geq 0$ and  $x\in \Omega\subset \mathbb R^n$
\begin{equation} \label{eq:mod1}
P^\varepsilon: \qquad 
\left\{\begin{array}{ll}
\ds\partial_t p^{\eps}+\frac{1}{\eps}\operatorname{div}(\uu^{\eps})=0,
& p^{\eps}\in \mathbb R, \\
\\
\ds\partial_t \uu^{\eps}+\frac{1}{\eps}\nabla
p^{\eps}=-\frac{\sigma}{\eps^2}\uu^{\eps},
& \uu^{\eps}  \in \mathbb R^n
 \end{array}\right.
\end{equation}
discretized with $P^0$ finite volume schemes.
This problem is representative
of many  transport problem such
as transfer and neutron transport,  for which the small parameter
$\eps$ is the ratio of two very different sound velocities and
$\sigma$ is the absorption or the opacity.
For simplicity both $\eps$ and  $\sigma>0$ are kept constant in space in this study.
The system (\ref{eq:mod1}) can also be introduced as a specific linearization
of a pressure-velocity system of partial differential equations
in the acoustic regime. In this work we will need the following well known energy estimates concerning 
the Cauchy problem for the partial differential equation (\ref{eq:mod1}): 
\begin{proposition}\label{bee}
If $\Omega= \mathbb R^n$ or $\Omega= \mathbb T^n$ and if the initial data $\V_0=(p_0,\uu_0) \in H^p( \Omega)$ then
\begin{equation}\label{bee1}
\vert\vert \V \vert \vert_{H^p( \Omega)}\leq \vert\vert \V_0 \vert \vert_{H^p( \Omega)}
\end{equation}
 and moreover 
\begin{equation}\label{bee2}
\frac{\sigma}{\eps^2}\vert\vert \uu \vert \vert^2_{L^2([0,T];H^p( \Omega))}\leq \vert\vert \V_0 \vert \vert^2_{H^p( \Omega)}.
\end{equation}
\end{proposition}
We will consider well prepared data in the sense that:
 $p^\eps(t=0)$
is independent of $\eps$ and is sufficiently smooth;
the initial velocity satisfies the equality in the second equation
of (\ref{eq:mod1}) at leading order. It writes 
\begin{equation} \label{eq:iniwp}
p^\eps(t=0)=p_0 \mbox{ and } 
\mathbf u^\eps(0)=-\frac\eps\sigma \nabla p_0.
\end{equation}
For such well prepared data, it can be easily shown that
the formal limit of $P^\varepsilon$ for small $\eps$ is
\begin{equation} \label{eq:mod2}
P^0: \qquad
\partial_t p - \frac1\sigma \Delta p=0. 
\end{equation}

\begin{remark}\label{sigmanotzero}
We do not consider the regime $\sigma \rightarrow 0$, since it introduces a singularity both
  in the initial data of the hyperbolic heat equation and in the limit parabolic equation.
\end{remark}

 Before addressing the main difficulty of this work  which is the discretization on  
  unstructured meshes, we briefly recall 
the  now well known notion 
of an asymptotic preserving technique \cite{jinbase}-\cite{jinreview}
which  is illustrated in the figure \ref{fig:diag1}.
For the simplicity of the presentation,
we will consider mainly semi-discrete numerical methods, this is why
the time step does not show up.
In  figure \ref{fig:diag1} the parameter $h$ designs a numerical method
with characteristic length $h\leq 1$:
so we assume  a numerical method $P_h^\varepsilon$ for the discretization
of $P^\varepsilon$.  
\begin{definition}[Uniform AP] \label{defAPu}
If  $P_h^\varepsilon$ is consistent with $P^\varepsilon$
uniformly with respect to $\varepsilon$, 
then we  say that the  scheme $P_h^\varepsilon$
is  uniformly AP  (uniformly asymptotic preserving).  
\end{definition}

@@

We define a  threshold value $\varepsilon_{\rm thresh} $
by  $\varepsilon_{\rm thresh}  ^{-b}h^c=
\eps_{\rm thresh}^a$. So either $\eps\leq \varepsilon_{\rm thresh} $
so that $\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)\leq \varepsilon_{\rm thresh} =h^{\frac{ac}{a+b}  }$, or 
$\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
taking the other term as the minimum.
And since $d\geq c$, one gets the abstract bound
$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
3Ch^{\frac{ac}{a+b}  }
$ which ends the proof.
\end{proof}
TEST POUR GITHUB

The structure of these  inequalities explains our strategy: that is we
prove separately each of these inequalities 
(\ref{eq:mod3}-\ref{eq:mod3-bis}) with care, so that
the inequalities $d\geq c$ and $e\geq a$  are true.
This part of the proof relies on specific hyperbolic
and parabolic numerical methods. Even if it is technical, 
the first three inequalities 
(\ref{eq:mod3}-\ref{eq:mod4}) do not yield additional difficulties
with respect to the state of the art. The proof of  inequality  (\ref{eq:mod3-bis})
is provided in 1D, and can be probably  be generalized 
straightforwardly on cartesian meshes in 2D and 3D.
On the other hand  our researches on proving 
   (\ref{eq:mod3-bis})
for  $\| P_h^\eps-P_h^0\|$  show 
a fundamental  obstruction in dimension greater than one on unstructured meshes   which was not expected
initially. 
%Indeed the study of this  inequality  is based
%on  comparison principles and a priori estimates. 
Since the main difficulty is related
to $P_h^0$, 
it motivates the definition
of a new  diffusion scheme. 
To this end we remark that another diffusion scheme is naturally
 defined
from $P_h^\varepsilon$ by {killing}
the derivative $\partial_t v_h$ in the discrete version
of the second equation of (\ref{eq:mod1}).
 {Killing} at the continuous level
the $\partial_t v$ is absolutely
equivalent to taking the formal limit $\varepsilon \rightarrow 0^+$.
But at the discrete level, 
it appears that it generates a new family of diffusion 
schemes, where
both parameters $h$ and $\eps$ are present. We 
call them Diffusion Asymptotic schemes, $DA_h^\varepsilon$.
By construction $P_h^0=\lim_{\varepsilon\rightarrow 0} DA_h^\varepsilon$. This 
is summarized
in figure \ref{fig:diag5}.
Finally since the scheme $DA_h^\eps$  is
 still  an accurate discretization of $P^0$,
our proof of the uniform AP properties is based
on the new AP diagram  displayed in figure \ref{fig:diag4}.

@@

\begin{proposition}\label{prodentrgosse}
The  scheme $P_h^\eps$
is stable in $L^2$ norm. Moreover, 
\begin{equation}\label{estiuepsflux}
\sqrt{
\int_0^T \left( \sum \Delta x_{j+\frac12}  ( u_{j+\frac12 }^\eps)^2 \right)dt
}
\leq
\frac{\eps}{\sqrt{\sigma}}
 \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}
\end{equation}
and
\begin{equation}\label{estiuepsflux2}
 \sqrt{
\int_0^T
\left(
\sum_{j\in \mathbb{Z}} 
{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }
 +\sum_{j\in \mathbb{Z}} 
{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }
\right)dt }
\leq \sqrt \eps  \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}.
\end{equation}
\end{proposition}
\begin{remark}
The strategy of the proof of many estimates in this work
consists to analyze the balance
between the dissipation of the fluxes and the physical dissipation (all 
 source terms like 
$-\frac\sigma{\eps^2}u$) on the one hand, and some truncation errors
on the other hand.
This is why it is  convenient
to reformulate $P_h^\eps$
so that   the pressure fluxes 
$p_{j+\frac12 }^{\eps}$ and $p_{j-\frac12 }^{\eps}$ are eliminated in the second
equation of (\ref{schema1}). This elimination is technically convenient since
all dissipation terms are expressed using the same variable, namely $u$.
It will simplify a lot the comparisons between
all kinds of dissipation terms and other errors terms.
\end{remark}

@@

Some similar bounds hold 
for  the quantities relatives to the diffusion scheme (\ref{schemadifff}).
First, multiplying the diffusion scheme by $p_j$ and adding on all the cells,
one has the $L^2$ stability in the sense
\begin{equation*}
\frac12 \frac{d}{dt}\sum_j \Delta x_jp_j^2=-\frac{1}{\sigma}\sum_j
\frac{(p_{j+1}-p_j)^2}{\Delta x_{j+\frac12 }}.
\end{equation*}
Thus 
the following estimate holds for
 the function 
$\bar{v}_h=\left( v_{j+\frac12}  \right)_j$ defined by
(\ref{eq:vv})

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme, assuming smooth initial data.
\eqref{schemadifff}. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

Using the definition of $u_j$
and $u_{j+\frac12 }$, one has 
$$
S_{j+\frac12 }=\frac{\eps}{2}\left( \frac{ \Delta x_j}{\Delta x_{j+\frac12}}
\frac{d}{dt} p_j - \frac{\Delta x_{j+1}}{\Delta x_{j+\frac12}} \frac{d}{dt} p_{j+1} \right)
$$
 at all time.
Moreover, $z_h=\frac{d}{dt} p_h$ is solution of
$P_h^0$:
$$
\Delta x_j\frac{d}{dt} z_j -\frac{1}{\sigma } \bigg(
\frac{z_{j+1}-z_j}{\Delta x_{j+\frac12 }}-\frac{z_j -z_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0,
$$
with initial condition
\begin{equation}\label{eq:zz}
z_j(0)=\frac{d}{dt} p_0(x_j)=
\frac1 {\Delta x_j \sigma } \bigg(
\frac{p_0(x_{j+1})-p_0(x_j)}{\Delta x_{j+\frac12 }}-\frac{p_0(x_j)
 -p_0(x_{j-1}  )}{\Delta
x_{j-\frac12 }}\bigg).
\end{equation}
One gets from a Taylor expansion with integral residue
that
$$
\left|
\frac{p_0( x_{j+1}) -p_0(x_j)}{\Delta x_{j+\frac12 }}- 
\partial_x p _0(x_j)
\right|\leq 
 \int_{x_j}^{x_{j+1}  } \left|\partial_{xx}p_0(y)   \right| dy .$$ 
Similarly one has the bound
$
\left|
 \frac{p_0( x_{j}) -p_0(x_{j-1})}{\Delta x_{j+\frac12 }}-
\partial_x p _0(x_j)\right|
\leq
 \int_{x_{j-1}}^{x_{j}  } \left|\partial_{xx}p_0(y)   \right| dy $.
Therefore $|z_j(0)|\leq
\frac1 {\Delta x_j \sigma }  \int_{x_{j-1}}^{x_{j+1}  } \left|\partial_{xx}p_0(y)  
 \right| dy $ from which the bound
$
\sqrt{ \sum_j \Delta x_j z_j^2(0) }
\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
is deduced.
Since the scheme $P_h^0$ being stable in $L^2$, this bound is true at any time.
Considering (\ref{eq:zz}) the discrete second derivative
attached to $P_h^0$ is bounded at any time, which ends the proof
of the claim.
\end{proof}

@@

The numerical approximation  
 of the problem  $\mathbf P^\eps$ that we study 
 is the JL-(b) scheme defined
in   \cite{glaceap}
\begin{equation}\label{eq:4}
\mathbf P_h^\eps:
\qquad \left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r} l_{jr} \njr    p_{jr}^{\eps}=-\frac{\sigma}{\varepsilon^{2}}\sum_{r}\widehat{
\beta}_{jr}\ur^{\eps},
\end{array}
\right.
\end{equation}
with initial data $p_j^{\eps}(0)=p_0(\mathbf{x}_j)$ and $\mathbf{u}_j^{\eps}(0) = -\eps\sigma^{-1}\nabla p_0(\mathbf{x}_j)$.
The fluxes are defined by the so-called 
corner problem 
\begin{equation}\label{eq:5}
\left\{ \begin{array}{l}
\displaystyle 
p_{jr}^{\eps}-p_j^\eps=
\njr,    \uj^{\eps}-\ur^{\eps}
)-\frac{\sigma}{\varepsilon}( \xr -\xj, \ur^{\eps}), 
\\
\sum_{j}\ljr
p_{jr}^{\eps}\njr=0.
 \end{array}\right.
\end{equation}
This corner problem has been introduced in 
\cite{glaceap} as a multidimensional version
of the 1D Jin-Levermore technique   \cite{jinlev}.
Its solution is provided by the solution
of the  linear system
\begin{equation*} \label{eq:5bis}
\displaystyle \left( \sum_{j}\alj+ 
\sum_{j}\frac{\sigma}{\varepsilon}\bej\right)\ur^{
\eps}= \sum_{j}\ljr
p_j^{\eps}\njr+\sum_j\alj\uj^{\eps},
\end{equation*}
 where the geometry of the mesh serves to define the  
  matrices  
$\alj$ and $\bej$ 
\begin{equation}\label{eq:6}
\alj=\ljr\njr\otimes\njr,\mbox{ and
}\bej=\ljr\njr\otimes(\xr-\xj) .
\end{equation}
We will use the notations
$A_j=\sum_r\alj$, $A_r=\sum_j\alj$ and
$B_r=\sum_j\bej$. 
By comparison with the scheme $P_h^\eps$ in dimension one, one see at once
that the multi-dimensional scheme (\ref{eq:4}-\ref{eq:6})  is  more 
tricky than the 1D scheme (\ref{schema1}-\ref{eq:fflux}).

@@

\begin{proposition}[Convergence]\label{ein_prosit}
There exist a constant $C(T, \sigma)>0$ 
      such that the following estimate holds
\begin{equation} \label{eq:veps2}
\|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
C(T, \sigma)\|  \mathbf V ^\eps (0) \|_  { H^3(\Omega)  }
\sqrt{\frac h \eps}.
\end{equation}
\end{proposition}
In the whole proof, we will use a constant $C>0$ large enough.
 Like in 1D, we use the method introduced by Mazeran \cite{Mazeran}. 
We introduce
$\mathscr{E}(t)=\frac12 \|\V^{\eps}-\V^{\eps}_h\|_{L^2(\Omega)}^2$.
As for the 1D proof and for the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $.

@@

\bibitem{Gosse} L. Gosse, G. Toscani \emph{An asymptotic-preserving
well-balanced scheme for the hyperbolic heat equations} C. R. Acad. Sci
Paris,Ser. I 334, pp  337-342, , 2000.

>>>>

We address the convergence analysis  on unstructured meshes
of diffusion
asymptotic preserving schemes for the discretization
of a problem with a stiff parameter denoted as $\eps\leq 1$.
The model problem considered in this work
is  the hyperbolic heat equation in the domain 
$t\geq 0$ and  $x\in \Omega\subset \mathbb R^n$
\begin{equation} \label{eq:mod1}
P^\varepsilon: \qquad 
\left\{\begin{array}{ll}
\ds\partial_t p^{\eps}+\frac{1}{\eps}\operatorname{div}(\uu^{\eps})=0,
& p^{\eps}\in \mathbb R, \\
\\
\ds\partial_t \uu^{\eps}+\frac{1}{\eps}\nabla
p^{\eps}=-\frac{\sigma}{\eps^2}\uu^{\eps},
& \uu^{\eps}  \in \mathbb R^n
 \end{array}\right.
\end{equation}
discretized with first order finite volume schemes.
This problem is representative
of many  transport problem such
as transfer and neutron transport,  for which the small parameter
$\eps$ is the ratio of two very different sound velocities and
$\sigma$ is the absorption or the opacity.
For simplicity both $\eps$ and  $\sigma>0$ are kept constant in space in this study.
The system (\ref{eq:mod1}) can also be introduced as a specific linearization
of a pressure-velocity system of partial differential equations
in the acoustic regime. In this work we will need the following well known energy estimates concerning 
the Cauchy problem for the partial differential equation (\ref{eq:mod1}): 
\begin{proposition}\label{bee}
If $\Omega= \mathbb R^n$ or $\Omega= \mathbb T^n$ and if the initial data $\V_0=(p_0,\uu_0) \in H^p( \Omega)$ then
\begin{equation}\label{bee1}
\vert\vert \V \vert \vert_{H^p( \Omega)}\leq \vert\vert \V_0 \vert \vert_{H^p( \Omega)}
\end{equation}
 and moreover 
\begin{equation}\label{bee2}
\frac{\sigma}{\eps^2}\vert\vert \uu \vert \vert^2_{L^2([0,T];H^p( \Omega))}\leq \vert\vert \V_0 \vert \vert^2_{H^p( \Omega)}.
\end{equation}
\end{proposition}
We will consider well prepared data in the sense that:
 $p^\eps(t=0)$
is independent of $\eps$ and is sufficiently smooth;
the initial velocity satisfies the equality in the second equation
of (\ref{eq:mod1}) at leading order. It writes 
\begin{equation} \label{eq:iniwp}
p^\eps(t=0)=p_0 \mbox{ and } 
\mathbf u^\eps(0)=-\frac\eps\sigma \nabla p_0.
\end{equation}
For such well prepared data, it can be easily shown that
the formal limit of $P^\varepsilon$ for small $\eps$ is
\begin{equation} \label{eq:mod2}
P^0: \qquad
\partial_t p - \frac1\sigma \Delta p=0. 
\end{equation}

\begin{remark}\label{sigmanotzero}
We do not consider the regime $\sigma \rightarrow 0$, since it introduces a singularity both
  in the initial data of the hyperbolic heat equation and in the limit parabolic equation.
\end{remark}
\subsection{Precision of AP discretizations}
 Before addressing the main difficulty of this work  which is the discretization on  
  unstructured meshes, we briefly recall 
the  now well known notion 
of an asymptotic preserving technique \cite{jinbase}-\cite{jinreview}
which  is illustrated in the figure \ref{fig:diag1}.
For the simplicity of the presentation,
we will consider mainly semi-discrete numerical methods, this is why
the time step does not show up.
In  figure \ref{fig:diag1} the parameter $h$ designs a numerical method
with characteristic length $h\leq 1$:
so we assume  a numerical method $P_h^\varepsilon$ for the discretization
of $P^\varepsilon$.  
\begin{definition}[Uniform AP] \label{defAPu}
If  $P_h^\varepsilon$ is consistent with $P^\varepsilon$
uniformly with respect to $\varepsilon$, 
then we  say that the  scheme $P_h^\varepsilon$
is  uniformly AP  (uniformly asymptotic preserving).  
\end{definition}

@@

We define a  threshold value $\varepsilon_{\rm thresh} $
by  $\varepsilon_{\rm thresh}  ^{-b}h^c=
\eps_{\rm thresh}^a$. So either $\eps\leq \varepsilon_{\rm thresh} $
so that $\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)\leq \varepsilon_{\rm thresh} =h^{\frac{ac}{a+b}  }$, or 
$\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
taking the other term as the minimum.
And since $d\geq c$, one gets the abstract bound
$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
3Ch^{\frac{ac}{a+b}  }
$ which ends the proof.
\end{proof}

\subsection{Organization of the proof}
The structure of these  inequalities explains our strategy: that is we
prove separately each of these inequalities 
(\ref{eq:mod3}-\ref{eq:mod3-bis}) with care, so that
the inequalities $d\geq c$ and $e\geq a$  are true.
This part of the proof relies on specific hyperbolic
and parabolic numerical methods. Even if it is technical, 
the first three inequalities 
(\ref{eq:mod3}-\ref{eq:mod4}) do not yield additional difficulties
with respect to the state of the art. The proof of  inequality  (\ref{eq:mod3-bis})
is provided in 1D, and can be probably  be generalized 
straightforwardly on cartesian meshes in 2D and 3D.
On the other hand  our researches on proving 
   (\ref{eq:mod3-bis})
for  $\| P_h^\eps-P_h^0\|$  show 
a fundamental  obstruction in dimension greater than one on unstructured meshes   which was not expected
initially. 
%Indeed the study of this  inequality  is based
%on  comparison principles and a priori estimates. 
Since the main difficulty is related
to $P_h^0$, 
it motivates the definition
of a new  diffusion scheme. 
To this end we remark that another diffusion scheme is naturally
 defined
from $P_h^\varepsilon$ by {killing}
the derivative $\partial_t v_h$ in the discrete version
of the second equation of (\ref{eq:mod1}).
 {Killing} at the continuous level
the $\partial_t v$ is absolutely
equivalent to taking the formal limit $\varepsilon \rightarrow 0^+$.
But at the discrete level, 
it appears that it generates a new family of diffusion 
schemes, where
both parameters $h$ and $\eps$ are present. We 
call them Diffusion Asymptotic schemes, $DA_h^\varepsilon$.
By construction $P_h^0=\lim_{\varepsilon\rightarrow 0} DA_h^\varepsilon$. This 
is summarized
in figure \ref{fig:diag5}.
Finally since the scheme $DA_h^\eps$  is
 still  an accurate discretization of $P^0$,
our proof of the uniform AP properties is based
on the new AP diagram  displayed in figure \ref{fig:diag4}.

@@

\begin{proposition}\label{prodentrgosse}
The  scheme $P_h^\eps$
is stable in $L^2$ norm. Moreover, 
\begin{equation}\label{estiuepsflux}
\sqrt{
\int_0^T \left( \sum \Delta x_{j+\frac12}  ( u_{j+\frac12 }^\eps)^2 \right)dt
}
\leq
\frac{\eps}{\sqrt{\sigma}}
 \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}
\end{equation}
and
\begin{equation}\label{estiuepsflux2}
 \sqrt{
\int_0^T
\left(
\sum_{j\in \mathbb{Z}} 
{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }
 +\sum_{j\in \mathbb{Z}} 
{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }
\right)dt }
\leq \sqrt \eps  \|\V^{\eps}_h(0)\|_{L^2(\mathbb{R})}.
\end{equation}
\end{proposition}
\begin{remark}
The strategy of the proof of many estimates in this work
consists in analyzing the balance
between the dissipation of the fluxes and the physical dissipation (all 
 source terms like 
$-\frac\sigma{\eps^2}u$) on the one hand, and some truncation errors
on the other hand.
This is why it is  convenient
to reformulate $P_h^\eps$
so that   the pressure fluxes 
$p_{j+\frac12 }^{\eps}$ and $p_{j-\frac12 }^{\eps}$ are eliminated in the second
equation of (\ref{schema1}). This elimination is technically convenient since
all dissipation terms are expressed using the same variable, namely $u$.
It will simplify a lot the comparisons between
all kinds of dissipation terms and other errors terms.
\end{remark}

@@

Some similar bounds hold 
for  the quantities related to the diffusion scheme (\ref{schemadifff}).
First, multiplying the diffusion scheme by $p_j$ and adding on all the cells,
one has the $L^2$ stability in the sense
\begin{equation*}
\frac12 \frac{d}{dt}\sum_j \Delta x_jp_j^2=-\frac{1}{\sigma}\sum_j
\frac{(p_{j+1}-p_j)^2}{\Delta x_{j+\frac12 }}.
\end{equation*}
Thus 
the following estimate holds for
 the function 
$\bar{v}_h=\left( v_{j+\frac12}  \right)_j$ defined by
(\ref{eq:vv})

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data.
. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

Using the definition of $u_j$
and $u_{j+\frac12 }$, one has 
$$
S_{j+\frac12 }=\frac{\eps}{2}\left( \frac{ \Delta x_j}{\Delta x_{j+\frac12}}
\frac{d}{dt} p_j - \frac{\Delta x_{j+1}}{\Delta x_{j+\frac12}} \frac{d}{dt} p_{j+1} \right)
$$
 at all time.
Moreover, $z_h=\frac{d}{dt} p_h$ is solution of
$P_h^0$:
$$
\Delta x_j\frac{d}{dt} z_j -\frac{1}{\sigma } \bigg(
\frac{z_{j+1}-z_j}{\Delta x_{j+\frac12 }}-\frac{z_j -z_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0,
$$
with initial condition
\begin{equation}\label{eq:zz}
z_j(0)=\frac{d}{dt} p_0(x_j)=
\frac1 {\Delta x_j \sigma } \bigg(
\frac{p_0(x_{j+1})-p_0(x_j)}{\Delta x_{j+\frac12 }}-\frac{p_0(x_j)
 -p_0(x_{j-1}  )}{\Delta
x_{j-\frac12 }}\bigg).
\end{equation}
One gets from a Taylor expansion with integral residue
that
$$
\left|
\frac{p_0( x_{j+1}) -p_0(x_j)}{\Delta x_{j+\frac12 }}- 
\partial_x p _0(x_j)
\right|\leq 
 \int_{x_j}^{x_{j+1}  } \left|\partial_{xx}p_0(y)   \right| dy .$$ 
Similarly one has the bound
$
\left|
 \frac{p_0( x_{j}) -p_0(x_{j-1})}{\Delta x_{j+\frac12 }}-
\partial_x p _0(x_j)\right|
\leq
 \int_{x_{j-1}}^{x_{j}  } \left|\partial_{xx}p_0(y)   \right| dy $.
Therefore $|z_j(0)|\leq
\frac1 {\Delta x_j \sigma }  \int_{x_{j-1}}^{x_{j+1}  } \left|\partial_{xx}p_0(y)  
 \right| dy $ from which the bound
$
\sqrt{ \sum_j \Delta x_j z_j^2(0) }
\leq \sigma^{-1}\|p_0\|_{H^2(\mathbb{R})}$
is deduced.
Since the scheme $P_h^0$ is stable in $L^2$, this bound is true at any time.
Considering (\ref{eq:zz}) the discrete second derivative
attached to $P_h^0$ is bounded at any time, which ends the proof
of the claim.
\end{proof}

@@

The numerical approximation  
 of the problem  $\mathbf P^\eps$ that we study 
 is the JL-(b) scheme defined
in   \cite{glaceap}
\begin{equation}\label{eq:4}
\mathbf P_h^\eps:
\qquad \left\{ 
\begin{array}{l}
\displaystyle \mid\Omega_{j}\mid\frac{d}{dt} p_{j}^{\eps}+\frac{1}{\varepsilon}
\sum_{r}(l_{jr}\ur^{\eps},\njr)=0\\
\displaystyle \mid
\Omega_{j}\mid\frac{d}{dt}\uj^{\eps}+\frac{1}{\varepsilon}
\sum_{r} l_{jr} \njr    p_{jr}^{\eps}=-\frac{\sigma}{\varepsilon^{2}}\sum_{r}\widehat{
\beta}_{jr}\ur^{\eps},
\end{array}
\right.
\end{equation}
with initial data $p_j^{\eps}(0)=p_0(\mathbf{x}_j)$ and $\mathbf{u}_j^{\eps}(0) = -\eps\sigma^{-1}\nabla p_0(\mathbf{x}_j)$.
The fluxes are defined by the so-called 
corner problem 
\begin{equation}\label{eq:5}
\left\{ \begin{array}{l}
\displaystyle 
p_{jr}^{\eps}-p_j^\eps=
\njr,    \uj^{\eps}-\ur^{\eps}
)-\frac{\sigma}{\varepsilon}( \xr -\xj, \ur^{\eps}), 
\\
\sum_{j}\ljr
p_{jr}^{\eps}\njr=0.
 \end{array}\right.
\end{equation}
This corner problem has been introduced in 
\cite{glaceap} as a multidimensional version
of the 1D Jin-Levermore technique   \cite{jinlev}.
Its solution is provided by the solution
of the  linear system
\begin{equation*} \label{eq:5bis}
\displaystyle \left( \sum_{j}\alj+ 
\sum_{j}\frac{\sigma}{\varepsilon}\bej\right)\ur^{
\eps}= \sum_{j}\ljr
p_j^{\eps}\njr+\sum_j\alj\uj^{\eps},
\end{equation*}
 where the geometry of the mesh is sued to define the  
  matrices  
$\alj$ and $\bej$ 
\begin{equation}\label{eq:6}
\alj=\ljr\njr\otimes\njr,\mbox{ and
}\bej=\ljr\njr\otimes(\xr-\xj) .
\end{equation}
We will use the notations
$A_j=\sum_r\alj$, $A_r=\sum_j\alj$ and
$B_r=\sum_j\bej$. 
By comparison with the scheme $P_h^\eps$ in dimension one, one sees at once
that the multi-dimensional scheme (\ref{eq:4}-\ref{eq:6})  is  more 
tricky than the 1D scheme (\ref{schema1}-\ref{eq:fflux}).

@@

\begin{proposition}[Convergence]\label{ein_prosit}
There exists a constant $C(T, \sigma)>0$ 
      such that the following estimate holds
\begin{equation} \label{eq:veps2}
\|\V^{\eps}_h-\V^{\eps}\|_{L^\infty( [0,T]\times L^2  (\Omega) )}\leq
C(T, \sigma)\|  \mathbf V ^\eps (0) \|_  { H^3(\Omega)  }
\sqrt{\frac h \eps}.
\end{equation}
\end{proposition}
In the whole proof, we will use a constant $C>0$ large enough.
 Like in 1D, we use the method introduced by Mazeran \cite{Mazeran}. 
We introduce
$\mathscr{E}(t)=\frac12 \|\V^{\eps}-\V^{\eps}_h\|_{L^2(\Omega)}^2$.
As for the 1D proof and for the sake of simplicity, for any quantity $q$,   $q'$ stands indifferently for  $\frac{d}{dt}q $ or $\partial_t q $.

@@

\bibitem{Gosse} L. Gosse, G. Toscani \emph{An asymptotic-preserving
well-balanced scheme for the hyperbolic heat equations} C. R. Acad. Sci
Paris,Ser. I 334, pp  337-342, , 2002.
